Rao-Blackwellized smoother for Conditionally Linear and Gaussian models

### 2016-11-13 TexArxiv/clgm.tex
New experiments

\section{Numerical experiments}
\label{sec:numerical:experiments}
\subsection{Simulated data}
This section highlights the performance of the additional Rao Blackwellisation steps for the two-filter and the FFBS approximations of the marginal smoothing distributions in the case where $J=2$. In each setting the transition matrix $Q$ is such that the states are prone to stay in the same regime  for many time steps as expected for the WTI crude oil data,  see Section~\ref{sec:exp}. First, the FFBS algorithm is applied to a simple one-dimensional model with:
\[
\pi(1)=\pi(2) = 1/2\\;\;d_1 = 0.5\;\; d_2 = 0;\;c_1= c_2 = 0 \eqsp,
\]
\[
Q = \begin{pmatrix}0.99 & 0.01\\ 0.03 & 0.97\end{pmatrix}\;\;T_1 = T_2 = 1\;\;\barH_1 = \barH_2= 0.05\eqsp,
\]
\[
B_1 = B_2 =1\;\;\barG_1 = 0.3\;\;\barG_2 = 0.1\eqsp.
\]
The two FFBS algorithms are used with $N = \tilde{N} = 50$ and the estimated posterior probabilities $\mathbb{P}(a_k=1|Y_{1:n})$ are compared to the estimation obtained with the proposed FFBS algorithm with $2000$ particles. Figure~\ref{fig:ffbs:posterior} illustrates that the algorithm with rejuvenation slightly improves the original algorithm in this simple case. 
\begin{figure}
\centering
\includegraphics[scale=.3]{FFBSplot.eps}
\caption{Estimated posterior probabilities by the two FFBS algorithms.}
\label{fig:ffbs:posterior}
\end{figure}
In addition, Table~\ref{fig:ffbs:RMSE} displays the RMSE for the estimation of the labels as a function of time with $100$ independent batches of data and shows that the additional rejuvenation step improves the performance of the algorithm (at time $i$, the estimated label is set to $1$ if the estimation of $\mathbb{P}(a_i|Y_{1:n})$ is greater than $0.5$ and to $2$ otherwise).

>>>>

\section{Numerical experiments}
\label{sec:numerical:experiments}
\subsection{Simulated data}
This section highlights the performance of the additional Rao Blackwellisation steps for the two-filter and the FFBS approximations of the marginal smoothing distributions in the case where $J=2$. In each setting the transition matrix $Q$ is such that the states are prone to stay in the same regime  for many time steps as expected for the WTI crude oil data,  see Section~\ref{sec:exp}. First, the FFBS algorithm is applied to a simple one-dimensional model with:
\[
\pi(1)=\pi(2) = 1/2\\;\;d_1 = 0.5\;\; d_2 = 0;\;c_1= c_2 = 0 \eqsp,
\]
\[
Q = \begin{pmatrix}0.99 & 0.01\\ 0.03 & 0.97\end{pmatrix}\;\;T_1 = T_2 = 1\;\;\barH_1 = \barH_2= 0.05\eqsp,
\]
\[
B_1 = B_2 =1\;\;\barG_1 = 0.3\;\;\barG_2 = 0.1\eqsp.
\]
The two FFBS algorithms are used with $N = \tilde{N} = 50$ and the estimated posterior probabilities $\mathbb{P}(a_k=1|Y_{1:n})$ are compared to the estimation obtained with the proposed FFBS algorithm with rejuvenation and $2000$ particles. Figure~\ref{fig:ffbs:posterior} illustrates that the algorithm with rejuvenation slightly improves the original algorithm in this simple case. 
\begin{figure}
\centering
\includegraphics[scale=.3]{FFBSplot.eps}
\caption{Estimated posterior probabilities by the two FFBS algorithms.}
\label{fig:ffbs:posterior}
\end{figure}
Figure~\ref{fig:ffbs:err} displays the mean estimation error over $100$ independent Monte Carlo runs. The estimation error is defined as the difference between the the estimation obtained with the proposed FFBS algorithm with rejuvenation and $2000$ particles and the estimation given by the two FFBS algorithms with $N = \tilde{N} = 50$.
\begin{figure}
\centering
\includegraphics[scale=.3]{err_est_ffbs.eps}
\caption{Posterior probabilities estimation error fo the two FFBS algorithms.}
\label{fig:ffbs:err}
\end{figure}
%In addition, Table~\ref{fig:ffbs:RMSE} displays the RMSE for the estimation of the labels as a function of time with $100$ independent batches of data and shows that the additional rejuvenation step improves the performance of the algorithm (at time $i$, the estimated label is set to $1$ if the estimation of $\mathbb{P}(a_i|Y_{1:n})$ is greater than $0.5$ and to $2$ otherwise).
